My title

### 2024-10-31 paper/paper.qmd
Project name fixed, model changed
Project name fixed, model changed

---
title: "The 2024 U.S. Presidential Election Forecast"
subtitle: "Multiple Linear Regression and Bayesian Models Accounting for Poll Quality"
author: Haowei Fan, Fangning Zhang, Shaotong Li
thanks: "Code and data are available at: https://github.com/HaoweiFan0912/The-2024-U.S.-Presidential-Election-Forecast"
date: 13/10/2024
contact: haowei.fan@mail.utoronto.ca
licence: MIT
date-format: long
abstract: "This study presents a forecast for the 2024 U.S. presidential election using aggregated poll data to predict support for key candidates. By implementing both linear and Bayesian models, we analyze poll data from diverse sources to assess how factors related to poll quality influence candidate support predictions. Our findings reveal possible outcome of election. Additionally, this paper includes an idealized polling methodology to demonstrate best practices in survey design and sample representation."
format: pdf
number-sections: true
bibliography: references.bib
toc: true
toc-title: "Table of Contents"
toc-depth: 2
toc-location: left
---

```{r}
#| include: false
#| warning: false
#| message: false
library(tidyverse)
library(knitr)
library(dplyr)
library(ggplot2)
library(patchwork)
raw_data <- read_csv(here::here("data/01-raw_data/raw_data.csv"))
```

# Introduction

The U.S. presidential election is a globally significant event, drawing substantial international attention due to its potential impact on economies, international relations, and pressing social issues, including climate change and human rights. As the world anticipates the 2024 U.S. electoral contest, predicting the election’s possible outcomes can provide critical insights for policymakers, businesses, and civil society groups. This study aims to forecast the level of support for leading candidates, specifically Kamala Harris and Donald Trump, using aggregated poll data and statistical modeling.

To provide a robust prediction, we utilize a “poll-of-polls” approach, combining polling data from multiple organizations at both national and state levels to enhance accuracy and stability in forecasted support. Our analysis applies both a linear regression model and a Bayesian approach, with a focus on the key parameter of each candidate's predicted vote share. By considering variations in pollster methodology and geographic distinctions, we account for the nuances of state-level political landscapes and the potential influence of polling organizations.

The results of our models reveal consistent patterns in voter support across both Harris and Trump. The linear model estimates a stable support rate for Donald Trump at approximately 47.8%, with similar results for Harris at 46.7%. The Bayesian model, which incorporates pollster and state-level random effects, yields slightly more conservative support estimates, predicting 47.9% for Trump and 46.0% for Harris. These findings suggest that, while both candidates maintain stable support, Trump holds a slight advantage. The consistency across both models underlines the importance of accounting for variability across polling methodologies and regional voter bases.

Beyond the immediate electoral forecast, this study contributes valuable insights for understanding how polling predictions can inform societal and international expectations. Predicting election outcomes allows global stakeholders—such as policymakers, investors, and international organizations—to anticipate and adapt to potential shifts in U.S. policy. For instance, a leadership change could bring alterations in U.S. positions on trade, climate commitments, and foreign policy, influencing global economic stability and strategic alliances. Additionally, our findings underscore the importance of transparency in polling methodologies, as well as the potential for more nuanced and accurate forecasts that consider the heterogeneity in polling sources and voter demographics.

This paper is organized as follows. The next section outlines the data collection and filtering processes, detailing the key variables and sources. Following that, we discuss our methodological framework, including the construction of the linear and Bayesian models. In the results section, we present the outcomes of both models, and a discussion explores the broader implications of these findings. Finally, the paper concludes with recommendations for future research and potential applications of these forecasting models in electoral studies.

# Data {#sec-data}

## Overview

This project leverages several R packages, including tidyverse[@tidyverse], rstanarm[@rstanarm], testthat[@testthat], readr[@readr], broom[@broom], ggplot2[@ggplot2], and posterior[@posterior], to clean, analyze, and visualize polling data for the 2024 U.S. presidential election forecast. The raw polling data was sourced from FiveThirtyEight's 2024 presidential election polls[@fivethirtyeight2024], providing a comprehensive foundation for our analysis. Together, these packages facilitate a reproducible approach to data handling, statistical modeling, and result presentation in this study.

## Raw data
raw data一共有52个variables，以及15891条样本。
去掉重复variables，以及无关紧要的url,还有全空的varibales后还剩下以下variables以及description。
部分重要的在此显示，不重要的在appendix。
```{r, echo=FALSE, message=FALSE, warning=FALSE}
#| label: tbl-main_columns
#| tbl-cap: "Main column descriptions of the raw data"

# Define the selected variable names
selected_variables <- c("poll_id", "pollster_id", "sponsor_ids", "pollster_rating_id", "numeric_grade", "pollscore", "methodology", "transparency_score", "state", "start_date", "end_date", "sponsor_candidate_id", "sponsor_candidate_party", "question_id", "sample_size", "population", "tracking", "created_at", "notes", "source", "internal", "partisan", "race_id", "cycle", "office_type", "election_date", "stage", "nationwide_batch", "ranked_choice_reallocated", "ranked_choice_round", "hypothetical", "party", "answer", "pct")

# Define their descriptions
variable_descriptions <- c(
  "Unique identifier for each poll conducted.",
  "Unique identifier for the polling organization conducting the poll.",
  "Unique identifier(s) for the sponsor(s) of the poll, typically organizations that fund the poll.",
  "Unique identifier for the pollster's rating within a rating system.",
  "A numeric rating given to the pollster to indicate their quality or reliability .",
  "A numeric value representing the score or reliability of the pollster in question .",
  "The method used to conduct the poll .",
  "A score reflecting the pollster's transparency about their methodology .",
  "The U.S. state where the poll was conducted or focused, if applicable.",
  "The date the poll began .",
  "The date the poll ended .",
  "Unique identifier for the candidate sponsored by the sponsoring organization (if applicable).",
  "The political party of the candidate sponsored by the sponsor (if applicable).",
  "Unique identifier for the question asked in the poll.",
  "The total number of respondents participating in the poll .",
  "The abbreviated description of the respondent group, typically indicating their voting status .",
  "Indicates whether the poll is part of a tracking series .",
  "The timestamp when the poll data was created or entered into the system .",
  "Any additional notes or comments related to the poll.",
  "The source from where the poll data was derived.",
  "Indicates whether the poll is conducted internally by a campaign or organization.",
  "Indicates whether the poll has partisan sponsorship or is conducted by a partisan organization.",
  "A unique identifier for the political race being polled .",
  "The election cycle in which the poll is conducted .",
  "The type of political office being polled .",
  "The date of the election the poll is related to .",
  "The stage of the election being polled .",
  "Indicates whether the poll is part of a nationwide batch.",
  "Indicates if ranked-choice voting reallocations have been applied in the results.",
  "The round of ranked-choice voting, if applicable.",
  "Indicates whether the poll is about a hypothetical match-up.",
  "The political party of the candidate in the poll .",
  "The response or answer choice given in the poll .",
  "The percentage of the vote or support that the candidate received in the poll ."
)

# Create a tibble with variable names and descriptions
variable_tibble <- tibble(
  Variable = selected_variables,
  Description = variable_descriptions
)

# Define the variables to extract for the table of selected variables
variables_to_extract <- c("poll_id", "pollscore", "numeric_grade", "transparency_score", "start_date", "end_date", "sample_size", "population", "hypothetical", "methodology", "pct")

# Extract the relevant rows from the tibble
extracted_tibble <- variable_tibble %>% filter(Variable %in% variables_to_extract)

# Create the table using kable for selected variables
kable(extracted_tibble)
```
所有variable的na值
```{r, echo=FALSE, message=FALSE, warning=FALSE}
#| label: tbl-variable_na
#| tbl-cap: "Number of Missing Values and Percentages for Variables"
# Calculate the number of missing values for each selected variable
na_counts <- sapply(raw_data[ , selected_variables], function(x) sum(is.na(x)))

# Calculate the percentage of missing values for each selected variable
na_percentages <- sapply(raw_data[ , selected_variables], function(x) mean(is.na(x)) * 100)

# Create a tibble for missing value counts and percentages
na_tibble <- tibble(
  Variable = names(na_counts),
  Missing_Values = na_counts,
  Percentage_Missing = round(na_percentages,2)
)

# Split the tibble into two halves for side-by-side display
na_tibble_1 <- na_tibble[1:ceiling(nrow(na_tibble)/2), ]
na_tibble_2 <- na_tibble[(ceiling(nrow(na_tibble)/2) + 1):nrow(na_tibble), ]

# Create the table using kable for missing values
kable(na_tibble)
```
重要的numerical variable的分布：
```{r, fig.pos="H", fig.width=22, fig.height=18}
#| warning: false
#| message: false
#| echo: false
#| label: fig-numdis
#| fig-cap: "Distribution of numerical varibales"
### Define Variables and Prepare Data ###
# Define the numeric variables to plot
numeric_variables <- c("pollscore", "numeric_grade", "transparency_score", "sample_size", "pct")

# Convert start_date and end_date to Date type
raw_data$start_date <- ymd(raw_data$start_date)
raw_data$end_date <- ymd(raw_data$end_date)

# Define the date variables to plot
date_variables <- c("start_date", "end_date")

### Create Plots for Numeric Variables ###
# Create a list to store plots
plots <- list()

# Loop through selected numeric variables and plot their distributions
for (variable in numeric_variables) {
  plots[[variable]] <- ggplot(raw_data, aes_string(x = variable)) +
    geom_histogram(binwidth = 0.7, fill = "#69b3a2", color = "black", alpha = 0.8) +
    labs(title = paste("Distribution of", variable), x = variable, y = "Frequency") +
    theme_minimal(base_size = 30) +
    theme(
      plot.title = element_text(hjust = 0.5, size = 12),
      axis.title = element_text(size = 10),
      axis.text = element_text(size = 10)
    )
}

### Create Plots for Date Variables ###
# Loop through selected date variables and plot their distributions
for (variable in date_variables) {
  plots[[variable]] <- ggplot(raw_data, aes_string(x = variable)) +
    geom_histogram(binwidth = 30, fill = "#69b3a2", color = "black", alpha = 0.8) +
    labs(title = paste("Distribution of", variable), x = variable, y = "Frequency") +
    theme_minimal(base_size = 30) +
    theme(
      plot.title = element_text(hjust = 0.5, size = 12),
      axis.title = element_text(size = 10),
      axis.text = element_text(size = 10)
    )
}

### Combine and Print Plots ###
# Combine all individual plots into one using patchwork with 2 columns and 4 rows
combined_plot <- wrap_plots(plots, ncol = 3, nrow = 3, heights = unit(rep(3, 4), "in")) +
  plot_annotation(
    theme = theme(
      plot.title = element_text(hjust = 0.5, size = 14)
    )
  )

# Print the combined plot
print(combined_plot)

```
接下来是categorical
```{r, fig.pos="H", fig.width=22, fig.height=8}
#| warning: false
#| message: false
#| echo: false
#| label: fig-catdis
#| fig-cap: "Distribution of categorical varibales"

### Plot distributions for categorical variables ###
# Define the categorical variables to plot
categorical_variables <- setdiff(variables_to_extract, c(numeric_variables, "start_date", "end_date"))
categorical_variables <- categorical_variables[categorical_variables != "methodology" ]
categorical_variables <- categorical_variables[categorical_variables != "poll_id" ]
# Create a list to store plots for categorical variables
categorical_plots <- list()

# Loop through categorical variables and plot their distributions
for (variable in categorical_variables) {
  plot <- ggplot(raw_data, aes_string(x = variable)) +
    geom_bar(fill = "#69b3a2", color = "black") +
    labs(title = paste(variable), x = variable, y = "Count") +
    theme_minimal() +
    theme(plot.title = element_text(hjust = 0.5))

  # Add plot to list
  categorical_plots[[variable]] <- plot
}

### Plot top 5 methodologies ###
# Extract top 5 methodologies by frequency
top_5_methodologies <- raw_data %>%
  count(methodology, sort = TRUE) %>%
  top_n(5) %>%
  pull(methodology)

# Create a new column to categorize methodologies into top 5 and 'Other'
raw_data$methodology_grouped <- ifelse(raw_data$methodology %in% top_5_methodologies, raw_data$methodology, 'Other')

# Plot the distribution of the top 5 methodologies plus 'Other'
methodology_plot <- ggplot(raw_data, aes(x = methodology_grouped)) +
  geom_bar(fill = "#69b3a2", color = "black") +
  labs(title = "Top 5 Methodologies and Others", x = "Methodology", y = "Count") +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5))

# Add methodology plot to categorical plots list
categorical_plots[["methodology_grouped"]] <- methodology_plot

# Combine all individual plots for categorical variables into one using patchwork
combined_categorical_plot <- wrap_plots(categorical_plots) +
  plot_annotation(title = "Distributions of Categorical Variables")

# Print the combined plot for categorical variables
print(combined_categorical_plot)

### Create a list for non-numeric variables ###
non_numeric_variables <- setdiff(variables_to_extract, numeric_variables)

```
#######注意，appendix其他的图还没画

## Measurement

Some paragraphs about how we go from a phenomena in the world to an entry in the dataset.

## Outcome variables

Add graphs, tables and text. Use sub-sub-headings for each outcome variable or update the subheading to be singular.

Some of our data is of penguins (@fig-bills), from @palmerpenguins.

```{r}

```

Talk more about it.

And also planes (@fig-planes). (You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)

```{r}

```

Talk way more about it.

## Predictor variables

Add graphs, tables and text.

Use sub-sub-headings for each outcome variable and feel free to combine a few into one if they go together naturally.

# Model

The goal of our modelling strategy is twofold. Firstly,...

Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-model-details].

## Model set-up

Define $y_i$ as the number of seconds that the plane remained aloft. Then $\beta_i$ is the wing width and $\gamma_i$ is the wing length, both measured in millimeters.

\begin{align} 
y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
\mu_i &= \alpha + \beta_i + \gamma_i\\
\alpha &\sim \mbox{Normal}(0, 2.5) \\
\beta &\sim \mbox{Normal}(0, 2.5) \\
\gamma &\sim \mbox{Normal}(0, 2.5) \\
\sigma &\sim \mbox{Exponential}(1)
\end{align}

We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.

### Model justification

We expect a positive relationship between the size of the wings and time spent aloft. In particular...

We can use maths by including latex between dollar signs, for instance $\theta$.

# Results

Our results are summarized in @tbl-modelresults.

```{r}

```

```{r}
```

# Discussion

## First discussion point {#sec-first-point}

If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.

## Second discussion point

Please don't use these as sub-heading labels - change them to be what your point actually is.

## Third discussion point

## Weaknesses and next steps

Weaknesses and next steps should also be included.

\newpage

\appendix

# Appendix {-}

# Additional data details
raw data 部分没有解释的varibale
```{r, echo=FALSE, message=FALSE, warning=FALSE}
#| label: tbl-remain_columns
#| tbl-cap: "Remaining column descriptions of the raw data"

# Define the variables to extract for the remaining variables
remaining_variables <- setdiff(selected_variables, variables_to_extract)

# Extract the relevant rows from the tibble for remaining variables
remaining_tibble <- variable_tibble %>% filter(Variable %in% remaining_variables)

# Create the table using kable for remaining variables
kable(remaining_tibble, caption = "Descriptions of Remaining Variables")
```
raw data里没画的图
```{r}
#to be done
```

# Model details {#sec-model-details}

## Posterior predictive check

In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check. This shows...

In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior. This shows...

```{r}

```

## Diagnostics

@fig-stanareyouokay-1 is a trace plot. It shows... This suggests...

@fig-stanareyouokay-2 is a Rhat plot. It shows... This suggests...

```{r}

```

\newpage

# References

>>>>

---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - First author
  - Another author
thanks: "Code and data are available at: [https://github.com/RohanAlexander/starter_folder](https://github.com/RohanAlexander/starter_folder)."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---
